\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-04-07 k-planar.tex
Done(?!)

  Let $x$ be a vertex of $G_0$, let $F_x$ be the corresponding face of $G_0^*$, and let $v_1,\ldots,v_s$ be the facial cycle of $F_x$.  Let $C:=w_1,\ldots,w_r$ be the subsequence of $v_1,\ldots,v_s$ consisting of only the nation vertices.  Since $x$ is incident to at most $d$ nations, $r\le d$. Call $C_x$ the \defin{nation cycle} of $F_x$. Note that if $r=1$ then the ``nation cycle'' has no edges, and if $r=2$ then the ``nation cycle'' has one edge. \note{DW}{Perhaps we shouldn't call it the ``nation cycle'' since it is not necessarily a cycle.}

  Let $G_1$ be a plane supergraph of $G_0^*$ obtained by adding the nation cycle of each face $F$ of $G_0$, and then triangulating each face with more than $d$ vertices on its boundary.  Each nation cycle \note{DW}{add `` of length at least 3''} is now a face of $G_1$, and no face of $G_1$ has more than $d$ vertices on its boundary. Let $\widehat{G}_1$ be the $d$-framed graph whose frame is $G_1$.

By definition, $V(G)=V(\widehat{G}_1)$. To prove the claim, it suffices to show that $E(G)\subseteq E(\widehat{G}_1)$.  Indeed, if $vw\in E(G)$ then the nation faces corresponding to $v$ and $w$ have a common vertex $x$ on their boundary. The vertex $x$ corresponds to a face $F_x$ in $G_0^*$ and the facial cycle of $F_x$ contains $v$ and $w$.  Therefore, the nation cycle $C_x$ of $F_x$ contains $v$ and $w$. Since $C_x$ bounds a face in $G_1$, $vw\in E(\widehat{G}_1)$.
\end{proof}

>>>>

  Let $x$ be a vertex of $G_0$, let $F_x$ be the corresponding face of $G_0^*$, and let $v_1,\ldots,v_s$ be the facial cycle of $F_x$.  Let $C:=w_1,\ldots,w_r$ be the subsequence of $v_1,\ldots,v_s$ consisting of only the nation vertices.  Since $x$ is incident to at most $d$ nations, $r\le d$. Call $C_x$ the \defin{nation cycle} of $F_x$. Note that if $r=1$ then the ``nation cycle'' has no edges, and if $r=2$ then the ``nation cycle'' has one edge. 
  % \note{DW}{Perhaps we shouldn't call it the ``nation cycle'' since it is not necessarily a cycle.}
  % \note{PM}{I'm happy to call it a nation cycle and then use sarcastic quotes for the two oddball cases.}

  Let $G_1$ be a plane supergraph of $G_0^*$ obtained by adding the nation cycle of each face $F$ of $G_0$, and then triangulating each face with more than $d$ vertices on its boundary.  Each nation cycle of length at least $3$ is now a face of $G_1$, and no face of $G_1$ has more than $d$ vertices on its boundary. Let $\widehat{G}_1$ be the $d$-framed graph whose frame is $G_1$.

By definition, $V(G)=V(\widehat{G}_1)$. To prove the claim, it suffices to show that $E(G)\subseteq E(\widehat{G}_1)$.  Indeed, if $vw\in E(G)$ then the nation faces corresponding to $v$ and $w$ have a common vertex $x$ on their boundary. The vertex $x$ corresponds to a face $F_x$ in $G_0^*$ and the facial cycle of $F_x$ contains $v$ and $w$.  Therefore, the nation cycle $C_x$ of $F_x$ contains $v$ and $w$. \note{PM}{I distinguished the length $2$ case here.} If $C_x$ has length $2$ then $vw\in E(G_1)\subseteq E(\widehat{G}_1)$.  If $C_x$ has length at least $3$ then $C_x$ bounds a face in $G_1$, so $vw\in E(\widehat{G}_1)$.
\end{proof}
